---
title: "Lab 0 - Xie"
author: "Jenny"
date: "August 29, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What years are included in this data set? What are the dimensions of the data frame and what are the variable or column names? How do these counts compare to Arbuthnot's? Are they on a similar scale?

```{r load-present-data, echo=TRUE}
source("http://www.openintro.org/stat/data/present.R")
present
dim(present)
names(present)
```

## Make a plot that displays the boy-to-girl ratio for every year in the data set. What do you see? Does Arbuthnot's observation about boys being born in greater proportion than girls hold up in the U.S.? Include the plot in your response.

```{r boy-to-girl ratio, echo=TRUE}
plot(x = present$year, y = present$boys / present$girls, type = "l")
```

## In what year did we see the most total number of births in the U.S.?
```{r most number, echo=TRUE}
max(present$boys + present$girls)
present$year[which.max(present$boys + present$girls)]
```

